Digital History in Finland, 1488-1828

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

fen <- fen %>% filter(publication_year >= min.year & publication_year <= max.year)
kun <- kun %>% filter(publication_year >= min.year & publication_year <= max.year)
df0 = bind_rows(fen, kun)
df0$catalogue = factor(c(rep("Fennica", nrow(fen)), rep("Kungliga", nrow(kun))))
```

@@

### General trends

Relevant summaries can be moved here and polished. Which figures at least ?

General trends (top authors etc):

@@

### Fennica vs. Kungliga

Alustavia vertailuja Kungligasta suhteessa Fennicaan.

 * Fennica pois lukien Suomi ?
 * Kungliga pois lukien Ruotsi ?
 * Julkaisumäärien tilastointeja yleisesti ja paikkakunnittain

@@

@@

@@

```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="430px"}
for (catal in unique(df0$catalogue)) {
  df2 <- subset(df0, catalogue == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
  p <- ggplot(df2, aes(y = paper.consumption.km2, x = publication_decade, shape = gatherings, linetype = gatherings))
  p <- p + geom_point(size = 4)
  p <- p + geom_smooth(method = "loess", size = 1, color = "black")
  p <- p + ggtitle("Paper consumption in time by gatherings")
  p <- p + xlab("Year")
  p <- p + ylab("Paper consumption (km2)")
  p <- p + guides(linetype = guide_legend(keywidth = 5), shape = guide_legend(keywidth = 5))
  p <- p + ggtitle(paste("Paper consumption\n(", catal, ")", sep = ""))
  print(p)
}

@@

Library catalogues contain rich metadata on...

>>>>

fen <- fen %>% filter(publication_year >= min.year & publication_year <= max.year)
kun <- kun %>% filter(publication_year >= min.year & publication_year <= max.year)
df0 = bind_rows(fen, kun)
df0$catalog = factor(c(rep("Fennica", nrow(fen)), rep("Kungliga", nrow(kun))))
```

@@

### General trends: Fennica vs. Kungliga

Relevant summaries can be moved here and polished. Which figures at least ? Just let me know and I will add.

@@

Alustavia vertailuja

 * Julkaisumäärien tilastointeja yleisesti ja paikkakunnittain
 * Fennica pois lukien Suomi ?
 * Kungliga pois lukien Ruotsi ?

@@

Title count per decade:

```{r publishingovertime, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
df2 <- df0 %>% group_by(publication_decade, catalog) 
p <- ggplot(df2, aes(publication_decade)) +
     geom_bar() + scale_y_log10() + facet_grid(catalog ~ .) +
     ggtitle("Title count timeline")
print(p)
```

@@

```{r papercompbyformat, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=7, fig.show="hold", out.width="430px"}
for (catal in unique(df0$catalog)) {
  dfs <- df0 %>% filter(!gatherings == "NA" & catalog == catal)

  res <- titlecount_timeline(dfs, "gatherings", nmin = 15, mode = "n") 
  print(res$plot + ggtitle(paste(catal, " (n)", sep = "")))

  res <- titlecount_timeline(dfs, "gatherings", nmin = 15, mode = "percentage") 
  print(res$plot + ggtitle(paste(catal, " (%)", sep = "")))
}
```

@@

```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=10, fig.height=8, fig.show="hold", out.width="430px"}
for (catal in unique(df0$catalog)) {
  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper.consumption.km2 = sum(paper.consumption.km2, na.rm = TRUE), n = n()) 
  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
  p <- ggplot(df2, aes(y = paper.consumption.km2, x = publication_decade, shape = gatherings, linetype = gatherings))
  p <- p + geom_point(size = 4)
  p <- p + geom_smooth(method = "loess", size = 1, color = "black")
  p <- p + ggtitle("Paper consumption in time by gatherings")
  p <- p + xlab("Year")
  p <- p + ylab("Paper consumption (km2)")
  p <- p + guides(linetype = guide_legend(keywidth = 5), shape = guide_legend(keywidth = 5))
  p <- p + ggtitle(paste("Paper consumption\n(", catal, ")", sep = ""))
  print(p)
}

@@

Library catalogs contain rich metadata on...
